\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-11 arch.tex
updates

\rx provides a formal framework described which details partitioning
in \cite{py10} and \cite{rajan12} and is not the focus of this
chapter. Coupled interaction between planning and the world on the
other hand, has a significant implication on how planning can be
integrated in such frameworks; here we show using the \eu planner can
be coupled to our framework. First we link concepts in \eu planning
with the \rx framework. Note that in the following treatise, we call
the formal semantic framework of \rx as the 'agent'. Reactors
constitute an entity within this agent and are standalone blocks of
inference.

@@

\item {\em Observation on the current state values}: This information
  propagates up in the reactor dependency graph at the synchronization
  phase and occurs at the beginning of every tick. During this phase
  the agent provides to each reactor updates on their {\em external}
  state variables for this tick and ask them to compute their {\em
    internal} state variables values for this same tick. By doing so
  we propagate a consistent view of that state of the world throughout
  all the reactors as time advance.

\item {\em Goals request on future state}: This information propagates
  down in the reactor graph. It reflects that, in order to satisfy own
  of its {\em internal} objectives, a reactor may have a plan that
  rely on future values of one of its {\em external} state. When such
  a plan is identified we ensure that this part of the plan is given
  as a goal to the owner of the given {\em external(s)} state variable(s).

@@

The choice of representation of state variables, observations and
goals is directly derieved to the timelines and tokens from europa. 
such representation is rich enough to allow the exchange of state
information in a formal and yet flexible way and its transaltion in
planning frameworks that have an explicit representation of time (such
as but not limited to europa) is often trivial.

The overall execution cycle of the agent is also abstracted as a
continuous planning/deliberation cycle between all the
reactors. At the agent interface level, each reactor provided
only two abstract calls that conceptualize their execution:

@@

\item \texttt{synchronize} that takes the last {\em external}
  observations as argument and will return the {\em internal}
  observations for this reactor or a failure report.

\item \texttt{step} that accept new goals requested (if any) on the
  {\em internal} timeline of this reactor and will execute one step of
  deliberation. The returned value indicates if a complete plan has
  been found and in that case will also provide the part of this plan
  applied to {\em external} timelines of this reactor.

@@

Both of these two deliberative functions have different scope and
temporal constraints. The \texttt{synchronize} call is considered as
atomic and will focus only on state inference from the current tick by
identifying the current value of the {\em internal} state variables
from the latest updates on the {\em external} variables. This process
will then propagate up in the reactor graph at any single tick to
ensure that all reactors are aware of the current state of the
world. \texttt{step} relates to a single decision step of the planning
process which is focused on the future evolution of the state
variables and it can take multiple steps spanning other multiple ticks
for a reactor to produce a plan that is both complete and valid. when
such plan is identified its {\em external} part is then dispatched to
the corresponding reactors which in turn can start their deliberation
\texttt{step}s in order to satisfy these new objectives. As a
consequence physical execution will occur as these goals and planning
propagate down in the reactor graph until they eventually become goals
for the lowest level reactor which -- instead of deliberating -- may
just transform this goal in a physical command execution.

The way the agent interleave planning \texttt{step}s and
synchronization for a single reactor is illustrated in
Fig.~\ref{fig:tick-exec}. Synchronization happens at every single tick
and will interrupt planning allowing this reactor to identify its
current state that can propagate through the reactor graph in order to
ensure t aconsitent view of the state of the world between all the
reactors.

@@

This view of the reactor has two parallel tasks allow for long
planning deliberation while ensuring that the state evolution
propagates through the agent as time advance. These two tasks 
intertwined together give the two natural flows (bottom-up for state
estimation and top to bottom for future plan) that we expect to see in
a control loop. As they are both conceptualized as inference processes
it is natural to implement a reactor based on generic automated
planning. For example in Fig. \ref{fig:agent}, appart \textsf{Shore
  comm.} and \textsf{Vehicle} acting as interfaces to the system,
every other reactors (colored in blue) are different instance of our
europa reactor differntiated only by their model and europa solver
configurations.

\subsection{The Europa deliberative reactor}
\label{sec:arch:europa}

>>>>

\rx provides a formal framework which details partitioning in
\cite{py10} and \cite{rajan12} and is not the focus of this
chapter. Coupled interaction between planning and the world on the
other hand, has a significant implication on how planning can be
integrated in such frameworks; here we show using the \eu planner can
be coupled to our framework. First we link concepts in \eu planning
with the \rx framework. Note that in the following treatise, we call
the formal semantic framework of \rx as the 'agent'. Reactors
constitute an entity within this agent and are standalone blocks of
inference.

@@

\item {\em Observation on current state values}: This information
  propagates \emph{up} in the reactor dependency graph at the
  synchronization phase and occurs at the beginning of every
  tick. During this phase the agent provides updates to each reactor
  on their {\em external} state variables for this tick so as they
  could compute their {\em internal} state variable values for this
  same tick. By doing so we propagate a consistent view of that state
  of the world throughout all the reactors as time
  advances. \comment{could do with a figure here}

\item {\em Goal request on future state}: This information propagates
  \emph{down} in the reactor dependency graph. In order to satisfy own
  {\em internal} objectives, a reactor may have a plan that relies on
  future values of one of its {\em external} state. When such a plan
  is identified the agent ensures that this part of the plan is given
  as a goal to the owner of the given {\em external} state
  variable(s). \comment{could do with a figure here}

@@

The choice of representation of state variables, observations and
goals is directly derived from \eu timelines and tokens.  While such a
rich representation allows exchange of state information in a formal
yet flexible manner, its translation into planning frameworks that
have an explicit representation of time (such as but not limited to
\eu) is often trivial.

\subsection{The Execution Cycle}
\label{sec:arch:exec}

The overall execution cycle of the agent is also abstracted out as a
continuous planning/deliberation cycle between all reactors. At the
agent interface level, each reactor provides only two abstract calls
that conceptualize execution:

@@

\item \texttt{synchronize} takes the last {\em external} observations
  as an argument and returns the {\em internal} observations for a
  reactor or a failure report.

\item \texttt{step} that accepts new goals requested (if any) on the
  {\em internal} timeline of a reactor and will execute one step of
  deliberation \comment{Might be good to articulate what ``one'' step
    looks like}. The returned value indicates if a complete plan has
  been found. If so this part \comment{what does 'this part' mean? Can
    we sketch a figure or make it more formal?} of the plan is
  provided to {\em external} timelines of this reactor.

@@

Both these deliberative functions have different scope and temporal
constraints. The \texttt{synchronize} call is considered as atomic and
will focus only on state inference for the current tick by identifying
the current value of {\em internal} state variables from the latest
updates on the {\em external} state variables. This process propagates
up in the reactor dependency graph at any single tick \comment{at
  every single tick??? maybe} to ensure that all reactors are aware of
the current state of the world. \texttt{step} relates to a single
decision step of the planning process which is focused on the future
evolution of state variables; it can take multiple steps spanning
multiple ticks for a reactor to produce a plan that is both complete
and valid. When such plan is identified \comment{how? Is there a
  terminating condition?} its {\em external} timeline(s) are then
dispatched to the corresponding reactors which own these times and
which in turn can start their own deliberation \texttt{step}s to
satisfy these new objectives. Consequently execution occurs as these
goals and plans propagate down in the reactor hierarchy until they
eventually become goals for the lowest level reactor which -- instead
of deliberating -- may just transform this goal into a command for
execution in hardware.

@@

The manner in which the agent interleaves planning \texttt{step}s and
synchronization for a single reactor is illustrated in
Fig.~\ref{fig:tick-exec}. Synchronization occurs at every tick
interrupting planning; this allows a reactor to identify its current
state that can propagate through the reactor hierarchy in order to
ensure a consistent view of the state of the world between all the
reactors.
% This view of a reactor has two parallel tasks allowing for long
% planning deliberation while ensuring that the state evolution
% propagates through the agent as time advance.
These intertwined tasks together provide two natural information flow
methods (bottom-up for state estimation and top-down for plan
projection) that we expect to see in a control loop. As they are both
inference-based processes it is natural to implement a reactor based
on generic automated planning. For example in Fig. \ref{fig:agent},
apart from \textsf{Shore comm.} and \textsf{Vehicle} acting as
interfaces to the system, every other reactor (in blue) are different
instances of a \eu reactor differentiated only by their model and \eu
solver configurations.

\subsection{The  \eu Deliberative Reactor}
\label{sec:arch:europa}
